\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\begin{document}
\title{EKF Estimation Project Writeup}
\author{Suhasini P R}    

\maketitle
\section{The Tasks}
\begin{enumerate}
\item Sensor Noise
\item Attitude Estimation
\item Prediction Step
\item Magnetometer Update
\item Closed Loop + GPS Update
\item Adding Your Controller
\end{enumerate}
\section{Rubric Points}
Here I will consider the rubric points individually and describe how I addressed each point in my implementation.

\subsection{Writeup}
\begin{itemize}
\item Provide a Writeup / README that includes all the rubric points and how you addressed each one. You can submit your writeup as markdown or pdf.


You're reading it! Below I describe how I addressed each rubric point and where in my code each point is handled.
\end{itemize}
\subsection{Implement Estimator}
\begin{itemize}
\item Determine the standard deviation of the measurement noise of both GPS X data and Accelerometer X data.

I just got the data from the Graph 1 and Graph 2 text files and calculated Standard deviation for all the values in excel.

\item Implement a better rate gyro attitude integration scheme in the UpdateFromIMU() function.

I used FromEuler$123\_$RPY to first convert the estimates to Quaternion and then used IntegrateBodyRate function to get the predicted Quaternion. I then got the pitch and yaw using Pitch() and Roll() functions in the Quaternion class

\item Implement all of the elements of the prediction step for the estimator.

My first step here was to complete the PredictState() function which was a simple integration after converting the acceleration from body frame to inertial frame

I then completed the GetRbgprime function. Here i just populated the values by referring to the Estimation for Quadrotors document given. The matrix is as follows:
\begin{align}
R'_{bg} = \left[
  \begin{array}{ccc}
    -\cos \theta \sin \psi&
    -\sin\phi \sin \theta \sin \psi - \cos \phi \cos \psi&
    -cos \phi \sin \theta \sin \psi + \sin \phi \cos \psi\\
    \cos \theta \cos \psi&
    \sin \phi \sin \theta \cos \psi - \cos \phi \sin \psi&
    \cos \phi \sin \theta \cos \psi + \sin \phi \sin \psi\\
    0&0&0
  \end{array}
  \right]
\end{align}

After this, I implemented the Predict function to calculate $g'(x_t, u_t, \Delta t)$ matrix and then used this in the standard EKF update. 
The math for $g'(x_t, u_t, \Delta t)$ matrix is taken from the Estimation For Quadrotors document as is as follows:
\begin{align}
  g'(x_t, u_t, \Delta t) &= 
&= \left [ \begin{array}{ccccccc}
      1 & 0 & 0 & \Delta t & 0 & 0 & 0\\
      0 & 1 & 0 & 0 & \Delta t & 0 & 0\\
      0 & 0 & 1 & 0 & 0 & \Delta t & 0\\
      0 & 0 & 0 & 1 & 0 & 0 & R'_{bg}[0:]u_t[0:3] \Delta t\\
      0 & 0 & 0 & 0 & 1  & 0 & R'_{bg}[1:]u_t[0:3] \Delta t\\
      0 & 0 & 0 & 0 & 0 & 1 &  R'_{bg}[2:]u_t[0:3] \Delta t\\
      0 & 0 & 0 & 0 & 0 & 0 & 1
    \end{array}
    \right]
\end{align}

I used the following equations to update the Covariance

\begin{align}
G_t = g'(u_t, x_t, \Delta t)
\end{align}
\begin{align}
\bar{\Sigma}_t = G_t\Sigma_{t-1}G_t^T + Q_t
\end{align}
\item Implement the magnetometer update
I assigned yaw component of ekfstate variable to zFromX and computed $h'(x_{t})$ as follows:
\begin{align}
  h'(x_t) = \left[\begin{array}{ccccccc}
      0&0&0&0&0&0&1
      \end{array}\right]
\end{align}
After this, the function calls the Update() function to perform update.

\item Implement the GPS update.
Similar to the previous rubric, I assigned teh pos and velocity components from ekfState to zFromX and computed $h'(x_{t})$ as follows:
\begin{align}
  h'(x_t) = \left[\begin{array}{ccccccc}
      1&0&0&0&0&0&0\\
      0&1&0&0&0&0&0\\
      0&0&1&0&0&0&0\\
      0&0&0&1&0&0&0\\
      0&0&0&0&1&0&0\\
      0&0&0&0&0&1&0\\                  
      \end{array}\right]
\end{align}
\end{itemize}
\subsection{Flight Evaluation}
\begin{itemize}
\item Meet the performance criteria of each step.

Its meeting!
\item De-tune your controller to successfully fly the final desired box trajectory with your estimator and realistic sensors.

Its meeting!. Although, the square is not perfect.
\end{itemize}
\end{document}
